О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-06 pps-linear-bound/pps-linear-lower-bound.tex
Language cosmetics

\begin{theorem}
	\label{thm:prime_with_desired_distance}
	For every $m \geq 3$, $n \geq m+1$, $d \geq 1$ there exists an \textbf{prime}
	integral point set $M\in\mathfrak{M}(m,n)$ which
	contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.
\end{theorem}

>>>>

\begin{theorem}
	\label{thm:prime_with_desired_distance}
	For every $m \geq 3$, $n \geq m+1$, $d \geq 1$ there exists a \textbf{prime}
	integral point set $M\in\mathfrak{M}(m,n)$ which
	contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.
\end{theorem}
